Figures

### 2021-06-01 figure.Rmd
edits: correct paths

source(here::here("empirical/figure_map.R"))

@@

source(here::here("theory/figure_n_patch.R"))
```

@@

source(here::here("theory/figure_p_branch.R"))
```

@@

source(here::here("empirical/figure_diversity.R"))
```

>>>>

source(here::here("code_empirical/figure_map.R"))

@@

source(here::here("code_theory/figure_n_patch.R"))
```

@@

source(here::here("code_theory/figure_p_branch.R"))
```

@@

source(here::here("code_empirical/figure_diversity.R"))
```
